Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-06-12 BD_radvel/kurosawa.tex
New RV measurements. Revisions done.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@740 25464f21-6099-402c-b30a-640f1d40d38b

In Section~\ref{sec:observation-reduction}. we describe the observations
and the data reduction. The results of radial velocity and rotational
velocity ($v\,\sin i$) measurements are presented in
Section~\ref{sec:Results}. We discuss the binary/multiplicity 
fraction indicated by our RV survey, and compare our results with
earlier works in Section~\ref{sec:Binary-fraction}, and give
our conclusions in Section~\ref{sec:Conclusions}.

@@

\begin{tabular}{llcccc}
\hline 
Object&
Sp.&
mass&
RV&
$v\sin i$&
Known multiple?\tabularnewline
&
&
$\left[\mathrm{M_{\odot}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
$\mathrm{M7^{c}}$&
$0.07^{\mathrm{d}}$&
$-6.3\pm1.9^{\mathrm{d}}$&
$16.8\pm2.7^{\mathrm{d}}$&
no\tabularnewline
GY 141&
$\mathrm{M8.5^{a}}$&
$0.02^{\mathrm{d}}$&
\ldots{}&
$6.0^{f}$&
no\tabularnewline
GY 310&
$\mathrm{M8.5^{c}}$&
$0.08^{\mathrm{a,d}}$&
\ldots{}&
$10.0^{f}$&
no\tabularnewline
USco 40&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$37.5^{f}$&
no\tabularnewline
USco 53&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$45.0^{f}$&
no\tabularnewline
USco 55&
$\mathrm{M5.5^{b}}$&
$0.10+0.07^{\mathrm{e}}$&
\ldots{}&
$12.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 66&
$\mathrm{M6^{b}}$&
$0.07+0.07^{\mathrm{e}}$&
$-4.4\pm0.6^{\mathrm{d}}$&
$27.5^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 67&
$\mathrm{M5.5^{b}}$&
$0.10^{\mathrm{e}}$&
\ldots{}&
$18.0^{f}$&
no\tabularnewline
USco 75&
$\mathrm{M6^{b}}$&
$0.07^{\mathrm{e}}$&
$-5.6\pm1.1^{\mathrm{d}}$&
$63.0^{f}$&
no\tabularnewline
USco 100&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.9\pm0.6^{\mathrm{d}}$&
$50.0^{f}$&
no\tabularnewline
USco 101&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
\ldots{}&
no\tabularnewline
USco 104&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
$16.0^{f}$&
no\tabularnewline
USco 109&
$\mathrm{M6^{b}}$&
$0.07+0.04^{\mathrm{e}}$&
$-3.8\pm0.7^{\mathrm{d}}$&
$6.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 112&
$\mathrm{M5.5^{b}}$&
$0.1^{\mathrm{e}}$&
\ldots{}&
$8.0^{f}$&
no\tabularnewline
USco 121&
$\mathrm{M6^{b}}$&
$0.02^{\mathrm{b}}$&
$-38.9\pm1.0^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
USco 128&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-3.0\pm1.6^{\mathrm{d}}$&
$0.0^{f}$&
no\tabularnewline
USco 130&
$\mathrm{M7.5^{e}}$&
$0.04^{\mathrm{e}}$&
\ldots{}&
$14.0^{f}$&
no\tabularnewline
USco 132&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.2\pm1.1^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
\hline
\end{tabular}

@@

@@

\begin{tabular}{lcrrrrr}
\hline 
Object&
Date&
HJD-2453100&
RV&
$\sigma_{\mathrm{RRV}}$&
$\overline{\mathrm{RV}}$&
$v\sin i$\tabularnewline
&
&
&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$\tabularnewline
\hline 
GY 5&
2004-Apr-24&
20.7198440&
$-6.14\pm0.84$&
0.68&
&
\tabularnewline
&
2004-May-07&
33.7721938&
$-5.96\pm0.60$&
0.34&
$-6.05\pm1.03$&
$16.5\pm0.6$\tabularnewline
GY 141&
2004-May-10&
36.6712108&
$-4.39\pm0.60$&
0.34&
&
\tabularnewline
&
2004-May-17&
43.6683007&
$-2.95\pm0.51$&
0.11&
$-3.67\pm0.79$&
$4.4\pm1.4$\tabularnewline
GY 310&
2004-Apr-24&
20.8373504&
$-4.83\pm0.74$&
0.54&
&
\tabularnewline
&
2004-May-09&
35.8224052&
$-8.43\pm0.51$&
0.11&
$-6.63\pm0.90$&
$11.1\pm6.0$\tabularnewline
USco 40&
2004-Apr-05&
1.7661754&
$-7.15\pm0.74$&
0.54&
&
\tabularnewline
&
2004-May-07&
33.7620554&
$-6.80\pm0.51$&
0.11&
$-6.98\pm0.90$&
$34.2\pm0.5$\tabularnewline
USco 53&
2004-Apr-04&
0.9036653&
$-7.27\pm0.93$&
1.21&
&
\tabularnewline
&
2004-May-02&
28.7394676&
$-5.43\pm0.74$&
0.55&
$-6.35\pm1.19$&
$40.0\pm0.6$\tabularnewline
USco 55&
2004-Apr-05&
1.8422807&
$-5.39\pm0.50$&
0.02&
&
\tabularnewline
&
2004-May-02&
28.8141198&
$-6.38\pm0.53$&
0.27&
$-6.38\pm0.73$&
$22.9\pm0.8$\tabularnewline
USco 66&
2004-Apr-05&
1.7972634&
$-5.32\pm0.57$&
0.29&
&
\tabularnewline
&
2004-May-02&
28.7956003&
$-6.41\pm0.65$&
0.42&
$-5.87\pm0.86$&
$25.9\pm1.2$\tabularnewline
USco 67&
2004-Apr-05&
1.7188620&
$-6.01\pm0.74$&
0.55&
&
\tabularnewline
&
2004-May-02&
28.7113799&
$-6.83\pm0.59$&
0.31&
$-6.42\pm0.90$&
$18.4\pm0.4$\tabularnewline
USco 75&
2004-Apr-04&
0.8840376&
$-6.75\pm0.67$&
0.44&
&
\tabularnewline
&
2004-May-07&
33.6065432&
$-9.88\pm1.94$&
1.88&
$-8.32\pm2.05$&
$55.6\pm3.0$\tabularnewline
USco 100&
2004-Apr-06&
1.8179138&
$-6.76\pm2.74$&
2.69&
&
\tabularnewline
&
2004-May-02&
28.7752928&
$-10.23\pm1.80$&
1.73&
$-8.47\pm3.28$&
$43.7\pm3.2$\tabularnewline
USco 101&
2004-Apr-04&
0.8120734&
$-4.22\pm0.87$&
0.71&
&
\tabularnewline
&
2004-May-02&
28.6591660&
$-6.07\pm0.69$&
0.48&
$-5.15\pm1.11$&
$19.1\pm0.3$\tabularnewline
USco 104&
2004-Apr-04&
0.7850385&
$-5.83\pm0.50$&
0.02&
&
\tabularnewline
&
2004-May-02&
28.6349480&
$-7.48\pm0.50$&
0.06&
$-6.66\pm0.06$&
$16.7\pm0.4$\tabularnewline
USco 109&
2004-Apr-05&
1.7453989&
$-4.15\pm0.52$&
0.16&
&
\tabularnewline
&
2004-May-07&
33.6304878&
$-4.41\pm0.50$&
0.03&
$-5.12\pm0.72$&
$8.6\pm1.2$\tabularnewline
USco 112&
2004-Apr-04&
0.8552168&
$-2.70\pm0.69$&
0.47&
&
\tabularnewline
&
2004-May-07&
33.5826368&
$-3.46\pm0.51$&
0.11&
$-3.08\pm0.86$&
$5.8\pm1.2$\tabularnewline
USco 121&
2004-Apr-24&
20.7059408&
$-39.47\pm0.51$&
0.11&
&
\tabularnewline
&
2004-May-02&
28.6969641&
$-42.43\pm0.50$&
0.02&
$-40.95\pm0.71$&
$17.6\pm1.3$\tabularnewline
USco 128&
2004-May-13&
39.7978276&
$-7.41\pm0.85$&
0.69&
&
\tabularnewline
&
2004-May-17&
43.6108024&
$-6.94\pm1.16$&
1.05&
$-7.18\pm1.44$&
$3.6\pm1.1$\tabularnewline
USco 130&
2004-May-09&
35.7724090&
$-4.83\pm0.54$&
0.21&
&
\tabularnewline
&
2004-May-13&
39.8538830&
$-4.95\pm0.74$&
0.55&
$-4.89\pm0.92$&
$15.2\pm1.1$\tabularnewline
USco 132&
2004-May-13&
39.8268683&
$-7.18\pm0.58$&
0.30&
&
\tabularnewline
&
2004-May-17&
43.6391138&
$-7.37\pm1.02$&
0.89&
$-7.28\pm1.17$&
$9.1\pm0.7$\tabularnewline
\hline
\end{tabular}

@@

\includegraphics[%
  clip,
  scale=1.3]{figures/radvel_all01.eps}

@@

\includegraphics[%
  clip,
  scale=1.3]{figures/radvel_all02.eps}

@@

The radial velocities of each object were determined by using the cross-correlation
function of the object spectrum with that of a template star which has
a similar spectra type. By visual inspection,
the wavelength ranges used for the cross-correlation calculations
are chosen by avoiding the regions of spectra affected by the telluric
lines, and defects and fringes (in near infrared) of the CCDs. The
radial velocities of objects with respect to the template are obtained
by measuring the location of the peak in the cross-correlation
function. The location of the peak is determined by fitting the
cross-correlation function by a function which consists of two gaussians 
(with a common centre) plus a constant term. LHS~49 (Proxima Cen, M5.5) was
chosen as the template for this purpose. The radial velocity of the
template object LHS~49 was obtained by measuring the wavelength shifts
of the prominent photospheric absorption features \ion{K}{i}~$\lambda\lambda$7664.911,~7698.974.
This gives us $\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$, which is
in good agreement with the earlier measurement of \citet{garcia-sanchez:2001}
who found $\mathrm{RV_{LHS49}=}-21.7\pm1.8\,\kmps$. The heliocentric
RV of each object can be then calculated by adding $\mathrm{RV_{LHS49}}$
with the RV of each object with respect to LHS~49. In the following
measurements of the heliocentric radial velocities, our measurement
($\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$) will be used for consistency.

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard HD~140538
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed échelle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}18.8\pm0.6\,\kmps$
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep{udry:1999}.

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainty of RV with respect to the template star. The
two consecutive measurements of RVs (from same nights) are used to
find the (absolute/heliocentric) RV of the night, and their uncertainties are obtained from
the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
Note that for finding a shift in the radial velocities from two
different epochs, only $\sigma_{\mathrm{RRV}}$ is important since one
only requires relative (with respect to a template) RV values.
The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
values of the objects in UScoOB are consistent with the earlier measurements
of \citet{muzerolle:2003} in Table~\ref{tab:literatures}.

@@

We have computed $p$ for all the objects, and have plotted the results 
as a histogram of the $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
(excluding the non-member USco~121; see explanation later). 
The figure clearly shows two distinctive populations: one on the left
(with small $-\log{p}$ values) occupied by the RV constant objects,
and one on in the right-most bin (with the largest $-\log{p}$)
occupied by the RV variable objects which have $p<10^{-3}$.  The
expected distribution of $p$ computed consistently with our
uncertainty measurements is also shown in the same figure. The RV
constant population on the left side reasonably matches the expected
curve. This reassures that our uncertainties in RV values are
reasonable, and an additional systematic error may not be necessary in
this analysis (but see Section~\ref{sec:Binary-fraction}). According
to the figure, there are four objects which show significant RV
variations out of 17 samples. They are GY~141, GY~310, USco~55, and
USco~104, and considered as our preliminary binary/multiple
candidates.  We will discuss the effect of the systematics error in detail, and
list our final binary/multiple candidates in Section~\ref{sec:Binary-fraction}.

@@

\begin{center}
\includegraphics[%
  clip,
  scale=0.63]{figures/chisq_hist.eps}
\end{center}

@@

Finally, the histogram of $\overline{\mathrm{RV}}$ for the objects in UScoOB
is given in Fig.~\ref{fig:vrad_histrogram}. The total number
of the objects is 14. Note that USco~121 is excluded from the graph
since it is identified as a non-member of the UScoOB association based
on the RV value (see Table~\ref{tab:summary_results}).  \citet{muzerolle:2003}
also found it to be a likely non-member based on the radial velocity
and the low lithium abundance. The distribution of the RVs in the
figure was fitted by a gaussian function. We found that the standard
deviation and the peak position of the radial velocity distribution
are $1.2\,\kmps$ and $-5.9\,\kmps$ respectively. The former is very
similar to the standard deviation (0.9~$\kmps$) of the radial velocity
distribution of 9 BDs and VLM objects in Cha~I found by \citet{joergens:2006b}.
They also studied the radial velocity distribution of more massive
25 T~Tauri stars in Cha~I, and found the standard deviations ($1.3\,\kmps$)
is not significantly different from that of the brown dwarfs and the
very low-mass objects. Unfortunately, we do not have the radial velocity
measurements of the higher mass counter parts (T~Tauri stars) in
Upper Sco OB association. This is planned for a near future investigation
as this is important for the study of the mass dependency of the kinematics
in a young stellar cluster.

According to the hydrodynamical simulations of a low-mass star-forming
cluster of \cite{bate:2003} which yields a stellar density of
$\sim10^{3}\,\mathrm{stars\, pc^{-3}}$, the rms dispersion (1-D)
of the stars and the BDs is $1.2\,\kmps$.  Similarly for the model
with a higher stellar density ($\sim10^{4}\,\mathrm{stars\,
pc^{-3}}$), the rms dispersion is 2.5~$\kmps$
(\citealt{bate:2005}). The standard deviation of
$\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our analysis is more
comparable the lower stellar density model.

@@

\includegraphics[%
  clip,
  scale=0.63]{figures/radvel_hist.eps}

>>>>

In Section~\ref{sec:observation-reduction}. we describe the
observations and the data reduction. The results of radial velocity
and rotational velocity ($v\,\sin i$) measurements are presented in
Section~\ref{sec:Results}. We discuss the binary/multiplicity fraction
indicated by our RV survey in Section~\ref{sec:Binary-fraction}, and
give our conclusions in Section~\ref{sec:Conclusions}.

@@

\begin{center}\begin{tabular}{llcccc}
\hline 
Object&
Sp.&
mass&
RV&
$v\sin i$&
Known multiple?\tabularnewline
&
&
$\left[\mathrm{M_{\odot}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
$\mathrm{M7^{c}}$&
$0.07^{\mathrm{d}}$&
$-6.3\pm1.9^{\mathrm{d}}$&
$16.8\pm2.7^{\mathrm{d}}$&
no\tabularnewline
GY 141&
$\mathrm{M8.5^{a}}$&
$0.02^{\mathrm{d}}$&
\ldots{}&
$6.0^{f}$&
no\tabularnewline
GY 310&
$\mathrm{M8.5^{c}}$&
$0.08^{\mathrm{a,d}}$&
\ldots{}&
$10.0^{f}$&
no\tabularnewline
USco 40&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$37.5^{f}$&
no\tabularnewline
USco 53&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$45.0^{f}$&
no\tabularnewline
USco 55&
$\mathrm{M5.5^{b}}$&
$0.10+0.07^{\mathrm{e}}$&
\ldots{}&
$12.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 66&
$\mathrm{M6^{b}}$&
$0.07+0.07^{\mathrm{e}}$&
$-4.4\pm0.6^{\mathrm{d}}$&
$27.5^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 67&
$\mathrm{M5.5^{b}}$&
$0.10^{\mathrm{e}}$&
\ldots{}&
$18.0^{f}$&
no\tabularnewline
USco 75&
$\mathrm{M6^{b}}$&
$0.07^{\mathrm{e}}$&
$-5.6\pm1.1^{\mathrm{d}}$&
$63.0^{f}$&
no\tabularnewline
USco 100&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.9\pm0.6^{\mathrm{d}}$&
$50.0^{f}$&
no\tabularnewline
USco 101&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
\ldots{}&
no\tabularnewline
USco 104&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
$16.0^{f}$&
no\tabularnewline
USco 109&
$\mathrm{M6^{b}}$&
$0.07+0.04^{\mathrm{e}}$&
$-3.8\pm0.7^{\mathrm{d}}$&
$6.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 112&
$\mathrm{M5.5^{b}}$&
$0.1^{\mathrm{e}}$&
\ldots{}&
$8.0^{f}$&
no\tabularnewline
USco 121&
$\mathrm{M6^{b}}$&
$0.02^{\mathrm{b}}$&
$-38.9\pm1.0^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
USco 128&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-3.0\pm1.6^{\mathrm{d}}$&
$0.0^{f}$&
no\tabularnewline
USco 130&
$\mathrm{M7.5^{e}}$&
$0.04^{\mathrm{e}}$&
\ldots{}&
$14.0^{f}$&
no\tabularnewline
USco 132&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.2\pm1.1^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
\hline
\end{tabular}\par\end{center}

@@

%==========================================
\begin{table*}

@@

\begin{center}\begin{tabular}{lcrrrrr}
\hline 
0.81&
Date&
HJD-2453100&
RV&
$\sigma_{\mathrm{RRV}}$&
$\overline{\mathrm{RV}}$&
$v\sin i$\tabularnewline
&
&
&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$\tabularnewline
\hline 
GY 5&
2004-Apr-24&
20.7198440&
$-6.77\pm2.02$&
1.96&
&
\tabularnewline
&
2004-May-07&
33.7721938&
$-6.02\pm0.85$&
0.68&
$-6.39\pm2.19$&
$16.5\pm0.6$\tabularnewline
GY 141&
2004-May-10&
36.6712108&
$-4.15\pm0.63$&
0.38&
&
\tabularnewline
&
2004-May-17&
43.6683007&
$-3.46\pm0.66$&
0.43&
$-3.81\pm0.91$&
$4.4\pm1.4$\tabularnewline
GY 310&
2004-Apr-24&
20.8373504&
$-5.27\pm0.92$&
0.77&
&
\tabularnewline
&
2004-May-09&
35.8224052&
$-8.19\pm0.71$&
0.51&
$-6.73\pm1.16$&
$11.1\pm6.0$\tabularnewline
USco 40&
2004-Apr-05&
1.7661754&
$-7.34\pm0.52$&
0.15&
&
\tabularnewline
&
2004-May-07&
33.7620554&
$-6.28\pm0.52$&
0.15&
$-6.81\pm0.74$&
$34.2\pm0.5$\tabularnewline
USco 53&
2004-Apr-04&
0.9036653&
$-8.27\pm0.70$&
0.50&
&
\tabularnewline
&
2004-May-02&
28.7394676&
$-7.22\pm0.63$&
0.39&
$-7.75\pm0.95$&
$40.0\pm0.6$\tabularnewline
USco 55&
2004-Apr-05&
1.8422807&
$-6.21\pm0.50$&
0.04&
&
\tabularnewline
&
2004-May-02&
28.8141198&
$-6.55\pm0.50$&
0.06&
$-6.38\pm0.71$&
$22.9\pm0.8$\tabularnewline
USco 66&
2004-Apr-05&
1.7972634&
$-7.24\pm0.95$&
0.81&
&
\tabularnewline
&
2004-May-02&
28.7956003&
$-8.38\pm1.32$&
1.22&
$-7.81\pm1.63$&
$25.9\pm1.2$\tabularnewline
USco 67&
2004-Apr-05&
1.7188620&
$-7.07\pm0.67$&
0.44&
&
\tabularnewline
&
2004-May-02&
28.7113799&
$-5.70\pm0.58$&
0.30&
$-6.38\pm0.88$&
$18.4\pm0.4$\tabularnewline
USco 75&
2004-Apr-04&
0.8840376&
$-6.80\pm0.70$&
0.50&
&
\tabularnewline
&
2004-May-07&
33.6065432&
$-6.16\pm0.78$&
0.60&
$-6.48\pm1.05$&
$55.6\pm3.0$\tabularnewline
USco 100&
2004-Apr-06&
1.8179138&
$-7.37\pm0.67$&
0.44&
&
\tabularnewline
&
2004-May-02&
28.7752928&
$-7.47\pm0.62$&
0.36&
$-7.42\pm0.91$&
$43.7\pm3.2$\tabularnewline
USco 101&
2004-Apr-04&
0.8120734&
$-3.25\pm0.66$&
0.44&
&
\tabularnewline
&
2004-May-02&
28.6591660&
$-5.03\pm0.60$&
0.32&
$-4.14\pm0.89$&
$19.1\pm0.3$\tabularnewline
USco 104&
2004-Apr-04&
0.7850385&
$-7.05\pm0.61$&
0.35&
&
\tabularnewline
&
2004-May-02&
28.6349480&
$-7.62\pm0.57$&
0.27&
$-7.33\pm0.83$&
$16.7\pm0.4$\tabularnewline
USco 109&
2004-Apr-05&
1.7453989&
$-4.72\pm0.50$&
0.07&
&
\tabularnewline
&
2004-May-07&
33.6304878&
$-4.70\pm0.51$&
0.09&
$-4.71\pm0.72$&
$8.6\pm1.2$\tabularnewline
USco 112&
2004-Apr-04&
0.8552168&
$-2.95\pm0.50$&
0.05&
&
\tabularnewline
&
2004-May-07&
33.5826368&
$-3.41\pm0.51$&
0.07&
$-3.18\pm0.71$&
$5.8\pm1.2$\tabularnewline
USco 121&
2004-Apr-24&
20.7059408&
$-40.76\pm0.90$&
0.74&
&
\tabularnewline
&
2004-May-02&
28.6969641&
$-42.48\pm0.54$&
0.20&
$-41.62\pm1.04$&
$17.6\pm1.3$\tabularnewline
USco 128&
2004-May-13&
39.7978276&
$-7.03\pm0.51$&
0.09&
&
\tabularnewline
&
2004-May-17&
43.6108024&
$-6.32\pm0.51$&
0.10&
$-6.68\pm0.72$&
$3.6\pm1.1$\tabularnewline
USco 130&
2004-May-09&
35.7724090&
$-3.92\pm0.94$&
0.80&
&
\tabularnewline
&
2004-May-13&
39.8538830&
$-3.90\pm0.67$&
0.45&
$-3.91\pm1.16$&
$15.2\pm1.1$\tabularnewline
USco 132&
2004-May-13&
39.8268683&
$-6.68\pm0.53$&
0.18&
&
\tabularnewline
&
2004-May-17&
43.6391138&
$-6.61\pm0.54$&
0.20&
$-6.64\pm0.76$&
$9.1\pm0.7$\tabularnewline
\hline
\end{tabular}\par\end{center}

@@

%\includegraphics[%
%  clip,
%  scale=1.3]{figures/radvel_all01.eps}
\includegraphics[%
  clip,
  scale=0.9]{figures/radvel_all01.eps}

@@

%\includegraphics[%
%  clip,
%  scale=1.3]{figures/radvel_all02.eps}
\includegraphics[%
  clip,
  scale=0.9]{figures/radvel_all02.eps}

@@

The radial velocities of each object were determined by using the cross-correlation
function of the object spectrum with that of a template star which has
a similar spectra type. By visual inspection,
the wavelength ranges used for the cross-correlation calculations
are chosen by avoiding the regions of spectra affected by the telluric
lines, and defects and fringes (in near infrared) of the CCDs. The
radial velocities of objects with respect to the template are obtained
by measuring the location of the peak in the cross-correlation
function. The location of the peak is determined by fitting the
section of the cross-correlation function around the peak by a second
order polynomial. LHS~49 (Proxima Cen, M5.5) was
chosen as the template for this purpose. The heliocentric radial velocity of the
template object LHS~49 was obtained by measuring the wavelength shifts
of the prominent photospheric absorption features \ion{K}{i}~$\lambda\lambda$7664.911,~7698.974.
This gives us $\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$, which is
in good agreement with the earlier measurement of \citet{garcia-sanchez:2001}
who found $\mathrm{RV_{LHS49}=}-21.7\pm1.8\,\kmps$. The heliocentric
RV of each object can be then calculated by adding $\mathrm{RV_{LHS49}}$
with the RV of each object with respect to LHS~49. In the following
measurements of the heliocentric radial velocities, our measurement
($\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$) will be used for consistency.

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard HD~140538
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed échelle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}18.18\pm0.62\,\kmps$
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep{udry:1999}.

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainty of RV with respect to the template star. 
To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
procedure: (1)~add random gaussian deviate noise to the object spectra using the
corresponding variance spectra, (2)~compute the cross-correlation
curve using the spectra with added noise and the template, (3)~measure
the RV by locating the peak, (4)~repeat 1--3 for 100 times, and compute the standard
deviation of the 100 RV values. This should provide a good estimate of
uncertainties in RVs cased by the uncertainties in the flux levels.
We have also used an alternative method of estimating
$\sigma_{\mathrm{RRV}}$ values as described in
(c.f.~\citealt{joergens:2006}. The standard deviations of the mean of
the two independent RV measurements obtained from the two consecutive
spectra taken in the same night were assigned as the uncertainties
($\sigma_{\mathrm{RRV}}$). Although not shown here, we found that the
results from the two methods agree each other quite well. 
Note that for finding a shift in the radial velocities from two
different epochs, only $\sigma_{\mathrm{RRV}}$ is important since one
only requires the relative (with respect to a template) RV values.
The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
two epochs are also given in the same table. 
%The $\overline{\mathrm{RV}}$
%values of the objects in UScoOB are consistent with the earlier measurements
%of \citet{muzerolle:2003} in Table~\ref{tab:literatures}.

@@

We have computed $p$ for all the objects (Table~\ref{tab:chisq_prob}),
and have plotted the results  
as a histogram of the $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
(excluding the non-member USco~121; see explanation later). 
The figure clearly shows two distinctive populations: one on the left
(with small $-\log{p}$ values) occupied by the RV constant objects,
and one on the right (with the large $-\log{p}$ values)
occupied by the RV variable candidates.  The
expected distribution of $p$ computed consistently with our
uncertainty measurements is also shown in the same figure. The RV
constant population on the left side reasonably matches the expected
curve. This reassures that our uncertainties in RV values are
reasonable, and an additional systematic error may not be necessary in
this analysis. 
The boundary ($p=10^{-3}$) between the RV variable and the RV
constants seems somewhat arbitrary, but here we simply adopt the
definition of \citet{maxted:2005}.  Based on this criteria, there are
four objects which show significant RV variations (out of 17 samples)
as one can see from the figure.   They are USco~112, USco~128,
USco~40, and USco~55, and considered as our preliminary binary/multiple 
candidates.  We will discuss the binary fraction and the expected binary
detection probability later in Section~\ref{sec:Binary-fraction}.

@@

\begin{center}
%\includegraphics[%
%  clip,
%  scale=0.63]{figures/chisq_hist.eps}
\includegraphics[%
  clip,
  scale=0.46]{figures/chisq_hist.eps}
\end{center}

@@

\caption{The $\chi^{2}$ probabilities ($p$) of each object being a RV constant,
listed in ascending order of $p$. The ellipses represent the boundary
($p=10^{-3}$) between RV constant objects and RV variable objects. }

\label{tab:chisq_prob}

\begin{center}\begin{tabular}{cc}
\hline 
obj.~ID&
$p$\tabularnewline
\hline 
USco~112&
$8.9\times10^{-8}$\tabularnewline
USco~128&
$1.3\times10^{-7}$\tabularnewline
USco~40&
$5.8\times10^{-7}$\tabularnewline
USco~55&
$2.4\times10^{-6}$\tabularnewline
$\cdots$&
$\cdots$\tabularnewline
USco~101&
$1.1\times10^{-3}$\tabularnewline
GY~310&
$1.6\times10^{-3}$\tabularnewline
USco~67&
$1.0\times10^{-2}$\tabularnewline
USco~53&
$9.8\times10^{-2}$\tabularnewline
USco~104&
$2.0\times10^{-1}$\tabularnewline
GY~141&
$2.3\times10^{-1}$\tabularnewline
USco~75&
$4.1\times10^{-1}$\tabularnewline
USco~66&
$4.4\times10^{-1}$\tabularnewline
GY~5&
$7.2\times10^{-1}$\tabularnewline
USco~132&
$7.9\times10^{-1}$\tabularnewline
USco~100&
$8.6\times10^{-1}$\tabularnewline
USco~109&
$8.6\times10^{-1}$\tabularnewline
USco~130&
$9.8\times10^{-1}$\tabularnewline
\hline
\end{tabular}\par\end{center}

Finally, the histogram of $\overline{\mathrm{RV}}$ for the objects in UScoOB
is given in Fig.~\ref{fig:vrad_histrogram}. The total number
of the objects is 14. Note that USco~121 is excluded from the graph
since it is identified as a non-member of the UScoOB association based
on the RV value (see Table~\ref{tab:summary_results}).  \citet{muzerolle:2003}
also found it to be a likely non-member based on the radial velocity
and the low lithium abundance. The distribution of the RVs in the
figure was fitted by a gaussian function. We found that the standard
deviation and the peak position of the radial velocity distribution
are $1.0\,\kmps$ and $-6.3\,\kmps$ respectively. The former is very
similar to the standard deviation (0.9~$\kmps$) of the radial velocity
distribution of 9 BDs and VLM objects in Cha~I found by \citet{joergens:2006b}.
They also studied the radial velocity distribution of more massive
25 T~Tauri stars in Cha~I, and found the standard deviations ($1.3\,\kmps$)
is not significantly different from that of the brown dwarfs and the
very low-mass objects. Unfortunately, we do not have the radial velocity
measurements of the higher mass counter parts (T~Tauri stars) in
Upper Sco OB association. This is planned for a near future investigation
as this is important for the study of the mass dependency of the kinematics
in a young stellar cluster.

According to the hydrodynamical simulations of a low-mass star-forming
cluster of \cite{bate:2003} which yields a stellar density of
$\sim10^{3}\,\mathrm{stars\, pc^{-3}}$, the rms dispersion (1-D)
of the stars and the BDs is $1.2\,\kmps$.  Similarly for the model
with a higher stellar density ($\sim10^{4}\,\mathrm{stars\,
pc^{-3}}$), the rms dispersion is 2.5~$\kmps$
(\citealt{bate:2005}). The standard deviation of
$\overline{\mathrm{RV}}$ ($1.0\,\kmps$) found in our analysis is more
comparable the lower stellar density model.

@@

%\includegraphics[%
%  clip,
%  scale=0.63]{figures/radvel_hist.eps}
\includegraphics[%
  clip,
  scale=0.46]{figures/radvel_hist.eps}
